Model estimation

### 2024-11-24 modelestimate.Rmd
actualnullmodelfix
draft discussion

---
title: "Model estimation"
author: "Verooo"
date: "2024-11-20"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

@@

@@

#n-degree related popularity effect (inPop) (earlier called popularity or popularity of alter effect), defined by the sum of the in-degrees of the others to whom i is tied,

@@

@@

First, I estimate a null model with only reciprocity and degree.

The maximum convergence ratio of the model is 0.084. The GOF on the
Indegree Distribution is zero**.** This indicates that the model is a
very bad fit for the data. This is not suprising since we ran a null
model without any network effects.ffects.

For all GOF plots compiled in one place, see here:
<https://treesdude.github.io/labjournal/finalGOF.html>

CHANGE Both reciprocity and density are significant for an alpha of
**NUMBER**.

Estimates and standard errors

Rate parameters:

0\. Rate parameter 2.117 ( 0.3561)

Other parameters:

1\. eval: outdegree (density) -2.6388 ( 0.1460) convergence t ratio:
0.0182

2\. eval: reciprocity 1.8035 ( 0.4343) convergence t ratio: -0.0668

**meaning of significance in RSiena** "It is important to mention that
significance in RSiena means something different than in conventional
statistics. In normal statistics, such as OLS-regression, significance
of estimates refers to the fact that they are not 0 (**RELEVANT?**). In
RSiena, however, it refers to the fact that the estimates were precisely
determined (Ripley et al. 2011). Going forward with this chapter,
significance will refer to this definition of significance." - Niels
Vullings

This model has a density parameter of **NUMBER**, suggesting that
"people generally do not want to have a dense network".

The reciprocity parameter of **NUMBER** indicates that "people like to
send ties back to people who have sent a tie to them."

@@

fsave(Model0, file ="estimated_M0")

```{r load M0 output, echo=FALSE}
Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
Model0

@@

This model additionally entails InPop, outAct, isolateNet as network
statistics.

"The model has a maximum convergence ratio of **0.17** and a Goodness of
Fit on the indegree distribution of **.002.**"

"Indegree Popularity (inPop) is defined as the extent to which people
who have a lot of indegrees are more popular to connect with. This
parameter is NUMBER, meaning that actors have a preference to connect
with actors who have a lot of indegrees. The parameter is significant
for an alpha of **NUMBER**."

"Outdegree Activity (outAct) has a value of **NUMBER**, but is not
significant. IsolateNet is significant andhas a value of NUMBER and
refers to the preference of remaining an isolate. As this value is
positive (\*IS IT??!\*\*), it means that people prefer to be an isolate
in the network."

Estimates and standard errors

Rate parameters:

0\. Rate parameter 3.3566 ( 0.5773)

Other parameters:

1\. eval: outdegree (density) -2.0862 ( 0.7050)

2\. eval: reciprocity 1.0894 ( 0.4144)

3\. eval: indegree - popularity 0.2549 ( 0.0439)

4\. eval: outdegree - activity -0.0936 ( 0.1301)

5\. eval: network-isolate 4.9645 ( 1.1146)

convergence t ratio:

```         
1
0.0232
```

```         
2
0.0467
```

```         
3
-0.0195
```

```         
4
-0.0423
```

```         
5
-0.061
```

```         
 -0.0617
```

@@

This model is partly similar to Model 1 but additionally holds the
network statistics sameX, diffXTransTrip, egoX & altX of the covariate
gender.

@@

Other parameters:    
1. eval outdegree (density)                 -1.8628  ( 1.1060   )    0.0703      
2. eval reciprocity                          1.3341  ( 0.4543   )   -0.0152      
3. eval indegree - popularity                0.2209  ( 0.0470   )   -0.0083      
4. eval outdegree - activity                -0.3017  ( 0.2287   )    0.0806      
5. eval network-isolate                      4.7507  ( 1.5194   )   -0.0379      
6. eval gender_RS alter                      0.3254  ( 0.2701   )    0.0411      
7. eval gender_RS ego                       -1.0642  ( 0.6055   )   -0.0400      
8. eval same gender_RS                       0.6637  ( 0.2685   )    0.0308      
9. eval transitive triplets diff. gender_RS  2.1787  ( 0.6027   )    0.0416   
```

@@

**CHANGE!!**

"For the structural network statistics we find similar results, in terms
of estimate size and significance, as in Model 1. However, the outdegree
activity parameter almost reaches significance (**-1.7135484**).

With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) **are not significant and thus
the estimate cannot be trusted**."

egoX and altX: model whether male or female scholars are more likely to
initiate or receive ties.

**sameX (Gender)**: Tests whether scholars prefer same-gender
collaborators (direct measure of gender homophily).\
model the general tendency for scholars to collaborate with same-gender
peers.

**Confirmation**:

-   Significant and positive coefficient for `sameX` in the RSiena
    output would confirm that gender homophily exists.

-   A non-significant or negative coefficient would disconfirm this
    hypothesis.

**Confirmation**:

-   Significant and positive coefficient for `sameX` in the RSiena
    output would confirm that gender homophily exists.

-   A non-significant or negative coefficient would disconfirm this
    hypothesis.

@@

@@

This model is partly similar to Model 2 but additionally holds the
network statistics egoX and altX for the main effect of department, to
control for differences in collaboration patterns between the two
departments.

@@

**CHANGE** !!!!

For the structural network statistics we find similar results, in terms
of estimate size and significance, as in Model 1. However, the outdegree
activity parameter almost reaches significance (**-1.7135484**).

With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) **are not significant and thus
the estimate cannot be trusted**."

Estimates and standard errors

Rate parameters:

0\. Rate parameter 3.1013 ( 0.5186)

Other parameters:

1\. eval: outdegree (density) -4.3233 ( 1.0871)

2\. eval: reciprocity 1.0725 ( 0.4174)

3\. eval: indegree - popularity 0.2122 ( 0.0517)

4\. eval: outdegree - activity -0.3364 ( 0.2182)

5\. eval: network-isolate 4.2006 ( 1.3007)

6\. eval: gender_RS alter 0.3356 ( 0.2659)

7\. eval: gender_RS ego -1.0066 ( 0.5121)

8\. eval: same gender_RS 0.6632 ( 0.2623)

9\. eval: transitive triplets diff. gender_RS 1.5479 ( 0.5403)

10\. eval: departm_RS alter 0.4141 ( 0.7546)

11\. eval: departm_RS ego -1.1573 ( 0.9148)

12\. eval: same departm_RS 2.7240 ( 0.7277)

@@

This model further builds on the prior model and also includes the
network statistics of the covariat H-index, namely **egoX, altX and
inPopX**.

"The last model has a maximum convergence ratio of **0.23** and a a
Goodness of Fit on the indegree distribution of **0.197**.

**CHANGE!!!**

"In this model, the parameters for density and reciprocity are still
significant, with values of **-1.98** (se = **0.71**) and **2.59** (se =
**0.38**) respectively, meaning that actors prefer sparse networks, but
do prefer to send ties to alters who have sent ties to them.

IsolateNet is still significant with a value of **3.23** (se =
**1.06**), implying that actors prefer to be isolates.

In this model, **indegree popularity squared** (b = **0.17**, se =
**0.21**) is no longer significant, implying that this might be
explained by other network statistics in the model.

The covariate statistics for gender show similar findings as Model 2,
namely that actors prefer to close triads with alters that have a
different score for gender (b = **1.51**, se = **0.44**).

The ego effect and alter effect for gender are **non-significant**, as
was the case in Model 2.

Lastly, Model 3 shows some significant results with regards to the
covariate network statistics for prestige. The prestige effect for
alters is positive, implying that people prefer to send ties to people
who have a higher amount of prestige (b = **0.042**, se = **0.0089**).

Additionally, the prestige effect for egos is negative, which indicates
that people who have higher prestige send less ties (b = **-0.030**, se
= **0.015**). **This is in line with theories of preferential attachment
and upward mobility, because as egos with higher prestige will are more
likely to receive request for collaboration rather then sending request
for collaboration.**

Interestingly enough, the indegree popularity statistic for prestige is
not significant (b = **-0.012**, se = **0.023**), implying that actors
who are more prestigious do not receive more indegrees."

About Hypothesis 4

modeling how the department of the actor (Sociology or Political
Science) influences their collaboration choices in terms of gender.

**Interaction1 = "departm_RS"**: This allows you to test how department
(Sociology vs Political Science) influences the probability of forming
collaborations, potentially differing by gender. This means that gender
homophily (whether a person collaborates more often with same-gender
peers) might be different in the two departments.

allows you to explore how **department** influences the likelihood of
**same-gender** collaborations (`sameX`), which is central to your
research question. If the **department variable** is acting as an
important covariate influencing collaboration patterns, this line
captures that effect.

testing how being in a particular department influences the likelihood
of collaborating with someone of the same gender. In other words, it
checks if the department modifies the strength of gender homophily
(`sameX`).

**Network Statistics**:

-   **egoX (h-index)**: Examines how the h-index of the focal scholar
    affects their collaboration behavior.

-   **altX (h-index)**: Examines how the h-index of potential
    collaborators affects their attractiveness as partners.

    Add `egoX` and `altX` effects for `HIndex_RS` to test if prestigious
    scholars are more likely to initiate or receive ties.

-   **inPopX (h-index)**: Assesses whether prestige increases the
    likelihood of being sought out as a collaborator.

**Confirmation**:

-   A significant negative interaction term between `sameX` and h-index
    statistics would confirm that prestige reduces the strength of
    gender homophily.

-   If h-index variables do not significantly influence `sameX`, this
    would disconfirm H3.

>>>>

---
title: "Model estimation"
author: "Verooo"
date: "2024-11-20"
output: html_document
bibliography: references.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

Note to self. Keep in mind: \
**meaning of significance in RSiena** "It is important to mention that
significance in RSiena means something different than in conventional
statistics. In normal statistics, such as OLS-regression, significance
of estimates refers to the fact that they are not 0 (**RELEVANT?**). In
RSiena, however, it refers to the fact that the estimates were precisely
determined (Ripley et al. 2011). Going forward with this chapter,
significance will refer to this definition of significance." - Niels
Vullings

@@

#in-degree related popularity effect (inPop) (earlier called popularity or popularity of alter effect), defined by the sum of the in-degrees of the others to whom i is tied,

@@

sameX (Gender): Tests whether scholars prefer same-gender collaborators (direct measure of gender homophily).
model the general tendency for scholars to collaborate with same-gender peers.

  Confirmation:

    Significant and positive coefficient for sameX in the RSiena output would confirm that gender homophily exists.

    A non-significant or negative coefficient would disconfirm this hypothesis.

@@

First, I estimated a null model with only reciprocity and degree. The
maximum convergence ratio of the model is 0.084. The GOF on the Indegree
Distribution is zero**.** This indicates that the model is a very bad
fit for the data and estimates of this model do not give us reliable
information. \
*For all GOF plots compiled in one place, see here:
<https://treesdude.github.io/labjournal/finalGOF.html>.\
*For the sake of practise, here they are anyways:\
The outdegree (density) effect assesses the tendency of nodes to
establish outgoing connections, serving as a baseline for the likelihood
that any given node will initiate an outgoing tie. In the context of
this study, these outgoing ties represent the initiation of
co-publications. The outdegree estimate is significant and negative (b =
-2.6388, SE = 0.1460), suggesting that a scholar's tendency to initiate
collaboration is low and dense networks are less sought after. The
reciprocity parameter id significant and positive (b = 1.8035, SE =
0.4343), which implies that directed ties are likely to be reciprocated.
Specific to our case, it describes that scholars tend to initiate
collaborations with those alters who sent a tie to them too.

@@

fsave(Model0, file ="estimated_M0")
```

```{r load M0 output, echo=FALSE}
Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
Model0
```

@@

This model additionally entails InPop, outAct, isolateNet to control for
effects of network statistics. The maximum convergence ratio of this
model is **0.17** and a Goodness of Fit on the indegree distribution is
**0.002.** Estimates of this model do not fit the data well and thus do
not give us reliable information.

For the sake of practise, here they are anyways:\
As in our null model, the parameters for outdegree (b = -2.0862, SE =
0.7050) and reciprocity (b = 1.0894, SE = 0.4144) remain significant and
unchanged on their 'direction'.

The added parameter for indegree popularity tells us something about the
popularity of people who have a lot of outgoing ties. In our model the
estimate for this parameter is significantly positive (b =0.2549, SE
=0.0439), suggesting that scholars specifically like to initiate
collaborations with those who have a lot of indegrees.

Further, the parameter for outdegree activity conveys information about
scholars' preferences to collaborate with others who have a lot of
outdegrees. In our case, the estimate is insignificant and cannot be
reliably interpreted.

Lastly, the network isolate parameter can be used to infer about
scholars' tendency to neither send nor receive ties. The estimate for
this parameter is significantly positive (b = 4.9645, SE = 1.1146) in
our model, indicating that the scholars of our sample tend to remain
isolates.

@@

This model is partly similar to Model 1 but additionally holds the
network statistics sameX, diffXTransTrip, egoX & altX of the covariate
gender. EgoX and AltX ought to indicate whether male or female scholars
are more likely to initiate or receive ties, while sameX models the
general tendency for scholars to collaborate with same-gender peers.

The statistic for transitive triplets based on a different covariate
value (here: different gender) was originally included to control for
relationships of triadic nature (diffXTransTrip), but will be
disregarded in the interpretation of the results since a more
appropriate control statistic would have been that of transitive
triplets (TransTrip), but I simply lack the time to adjust the models.

@@

Other parameters:    
1. eval outdegree (density)                 -1.8628  ( 1.1060   )    0.0703 --> insign. (-1.684268)    
2. eval reciprocity                          1.3341  ( 0.4543   )   -0.0152 --> sign.    (2.936606)***     
3. eval indegree - popularity                0.2209  ( 0.0470   )   -0.0083 --> sign.    (4.7)     ***
4. eval outdegree - activity                -0.3017  ( 0.2287   )    0.0806 --> insign. (-1.319195)    
5. eval network-isolate                      4.7507  ( 1.5194   )   -0.0379 --> sign.    (3.126695)***

6. eval gender_RS alter                      0.3254  ( 0.2701   )    0.0411 --> insign.  (1.204739)      
7. eval gender_RS ego                       -1.0642  ( 0.6055   )   -0.0400 --> insign. (-1.757556)     
8. eval same gender_RS                       0.6637  ( 0.2685   )    0.0308 --> sign.    (2.471881)***     
9. eval transitive triplets diff. gender_RS  2.1787  ( 0.6027   )    0.0416 --> sign.    (3.6149)  ***
```

@@

Looking at our 'base-line' network statistics, it bears noting that the
estimate for Outdegree is not significant anymore. This statistic's
prior significance can seemingly be explained by a parameter relating to
the covariate gender that I added to this model. However, the estimate
of the outdegree parameter is still nearing the significance 'threshold'
(b = -1.8628, SE = 1.1060, b/SE = -1.684268).

Comparing this model to the prior ones, we see that the reciprocity
estimate is still significantly positive (b = 1.3341, SE = 0.4543).

The parameters of the structural network statistics also show similar
patterns in estimates and significance as they did in model 1.

Concerning the added covariate "gender", we find that the parameter
estimates for both covariate-related activity (egoX) , pertaining to the
gender of the ego, and covariate-related popularity (altX), relating to
the gender of the alter, do **not** show any significance and hence do
not allow for reliable inferences.

The 'same-covariate' measure (sameX) for gender is significantly
positive (b = 0.6637, SE =0.2685). It reveals that scholars, indeed,
prefer same-gender collaborators. This supports H1, which posits gender
homophily in collaboration patterns.

Model 2 provides strong evidence for gender homophily (H1), with
scholars more likely to collaborate with same-gender peers, but no
significant differences in collaboration tendencies based on the gender
of ego or alter.

@@

--\> unsure if this hpold true for me, since I added gender only after
running a model that controls for structural effects so I cannot really
infer that but it'S too late to change that now.

@@

This model is partly similar to Model 2 but additionally holds the
network statistics egoX and altX for the main effect of department, to
investigate differences in same-gender collaboration patterns based on
the two departments.

Originally, I planned to also include an interaction term of departm_RS
and gender_RS to obtain clearer insights into variations in patterns of
gender homophily in relation to scholars' departments. However, I have
refrained from adding another model to this project. I decided against
this partly due to time constraints but I also reason that I can use the
comparison of model 2 and 3 to examine changes in the estimate of
'sameX' (gender), to *tentatively* infer whether the department of
scholars modifies the collaboration patterns at hand.

@@

Interestingly, the estimate for outdegree (density) that had lost its
significance in model 2, is now back to being significant and negative
(b = -4.3233, SE = 1.0871).

In terms of estimate size and significance of the structural network
statistics we, once again, find similar patterns as in models 1 and 2.
However, the outdegree parameter has now reached significance (b =
-4.3233, SE = 1.0871).

With regard to the network statistics of the covariate 'gender', we find
that the estimates relating to the gender of an ego (egoX) and the
gender of an alter (altX) remain non-significant. The parameter
estimates for sameX remains significantly positive (b = 0.6632, SE =
0.2623) and are almost identical to those of model 2 (b = 0.6632, SE =
0.2623). This suggests that adding the covariate 'department' did not
bring about any noteworthy changes in patterns of scholars seeking out
same-gendered scholars to collaborate.

When it comes to the parameters pertaining to the added covariate
'department', we find that any differences in collaboration based on the
department of an ego (egoX) or of an alter (altX) are not warranted, as
the estimates of these parameters are insignificant. However, we find a
significantly positive estimate for the parameter of 'covariate-related
identity' (sameX), which indicates that scholars are more likely to
collaborate with people from their own department, indicating
**department-based homophily**. (b = 2.7240, SE = 0.7277).

Model 3 highlights persistent gender homophily (H1) across departments
but does not provide evidence for differences in gender homophily
between Sociology and Political Science, contrary to H2.

------------------------------------------------------

Estimates and SEs model 3:

1\. eval: outdegree (density) -4.3233 ( 1.0871) \*\*\*

2\. eval: reciprocity 1.0725 ( 0.4174) \*\*\*

3\. eval: indegree - popularity 0.2122 ( 0.0517) \*\*\*

4\. eval: outdegree - activity -0.3364 ( 0.2182) insign. (-1.541705)

5\. eval: network-isolate 4.2006 ( 1.3007) \*\*\*

6\. eval: gender_RS alter 0.3356 ( 0.2659) insign (1.262129)

7\. eval: gender_RS ego -1.0066 ( 0.5121) insign (-1.965632) almost
significant

8\. eval: same gender_RS 0.6632 ( 0.2623) sign. (2.52840) \*\*\* \
(sameX: comparison model 2 and 3:\
estimate got hardly any smaller (0.6637--\>0.6632), SE got hardly any
smaller (0.2685--\>0.2623), significance value got bigger
(2.47881--\>2.52840))

9\. eval: tr. tripl. diff. gend. 1.5479 ( 0.5403) sign. (2.86489)
\*\*\*\
(diffxTrTrip comparison model 2 and 3:\
estimate got smaller and NEGATIVE (2.1787 –\>-1.5479), SE got smaller
(0.6027 –\> 0.5403), significance value got smaller (3.6149--\>2.86489))

10\. eval: departm_RS alter 0.4141 ( 0.7546) insign. (0.549)

11\. eval: departm_RS ego -1.1573 ( 0.9148) insign (-1.27)

12\. eval: same departm_RS 2.7240 ( 0.7277) \*\*\*

@@

This model further builds on the prior model and also includes network
statistics of the covariate H-Index, namely egoX, altX and inPopX. By
adding these effects we can model how the h-index of a scholar
influences their preferences regarding same-gendered collaborations.
Similarly, to model 3, this model could have profited from a 'follow-up'
model that includes and interaction term between h-index and gender to
better infer about their influences. The same reasoning for my decision
to stick with one model prior also applies to this case. EgoX for this
covariate examines how the h-index of a scholar affects their
collaboration behavior, while AltX examines how the h-index of potential
collaborators affects their attractiveness as partners. With the help of
these effects we can test prestigious scholars are more likely to
initiate or receive ties. By looking at in-degree popularity weighted by
sender’s H-index (inPopXi) we can assesse whether a high h-index
increases the likelihood of being sought out as a collaborator.\

```         
Estimates, standard errors and convergence t-ratios
                                               Estimate   Standard   Convergence
                                                          Error      t-ratio
Rate parameters:  
  0      Rate parameter                       2.6891  ( 0.3675   )

Other parameters:     
   1. eval outdegree (density)                 -2.7693  ( 1.9205   )    0.0698 --> insign. (-1.441968)       
   2. eval reciprocity                          2.1770  ( 0.5960   )    0.0919 --> sign.    (3.652685)***      
   3. eval indegree - popularity               -0.0653  ( 0.1654   )   -0.0104 --> insign. (-0.3948005)      
   4. eval outdegree - activity                -0.6851  ( 0.4029   )    0.0527 --> insign. (-1.700422)      
   5. eval network-isolate                      5.4634  ( 2.2770   )    0.0028 --> sign.    (2.399385)***      
   6. eval gender_RS alter                     -0.0903  ( 0.3372   )    0.0129 --> insign. (-0.2677936)       
   7. eval gender_RS ego                        0.2993  ( 0.4934   )   -0.0503 --> insign. (0.6066072)      
   8. eval same gender_RS                       0.6820  ( 0.2804   )    0.0201 --> sign.   (2.43224)  ***       
   9. eval transitive triplets diff. gender_RS  2.4871  ( 0.6670   )    0.0505 --> sign.   (3.728786) ***    
  10. eval departm_RS alter                     0.3929  ( 0.6128   )   -0.0061 --> insign. (0.6411554)    
  11. eval departm_RS ego                      -1.4652  ( 0.6963   )   -0.0115 --> SIGN.   (-2.104265)***
  12. eval same departm_RS                      2.6327  ( 0.6080   )    0.0173 --> sign    (4.330099) ***    
  13. eval h_index_RS alter                     0.0829  ( 0.0364   )   -0.0031 --> SIGN    (2.277473) ***
  14. eval h_index_RS ego                      -0.1591  ( 0.0744   )    0.0161 --> SIGN.  (-2.138441) ***   
  15. eval ind. pop.^(1/1) weighted h_index_RS -0.0287  ( 0.0570   )   -0.0129 --> insign.(-0.5035088)
```

Model 4 has a maximum convergence ratio of **0.23,** and a a Goodness of
Fit on the indegree distribution of **0.197**.

Structural network statistics:

The estimate for outdegree is negative but not significant. This
suggests that, after accounting for other variables, the baseline
likelihood of forming ties remains low and is not a major driver of
collaboration patterns. Reciprocity has a significant positive estimate
(b = 2.1770, SE = 0.5960). This reflects a strong tendency for mutual
collaborations, meaning if one scholar collaborates with another, the
latter is likely to collaborate back (dyadic reciprocity). The paramters
Indegree Popularity and Outdegree Activity are both insignificant,
suggesting that neither the tendency to receive many collaborations
(indegree popularity) nor the tendency to initiate them (outdegree
activity) is significantly relevant to the network structure. The
network isolate estimate is, once again, significantly positive ( b =
5.4634, SE = 2.2770), indicating that as isolates tend to remain
isolated.

Gender:

Similar to AltX and EgoX in prior models, both an alter's gender (b =
-0.0903, SE = 0.3372) and an ego's gender (b = 0.2993, SE = 0.4934)
still have insignificant effects. The parameter SameX shows a
significant positive estimate (b = 0.6820, SE = 0.2804) which barely
differs from the two prior models. This suggests that adding the
covariate 'H-Index' did not prompt any major changes in scholars'
preferences for same-gendered collaborators.

Department:

While an alter's departmen**t** (AltX) remained insignificant to the
collaboration patterns, the estimates for an ego's department changed
incomparison to the prior model. In this model, egoX seems to be of
significant relevance (b = -1.4652, SE = 0.6963), with its negative
estimate indicating that, once effects of h-index are controlled for,
scholars from the political science (coded as 1) department have a lower
tendency to initiate collaborations than scholars from the sociology
department (coded as 0). \
Similar to the prior model, the sameX parameter for department shows a
significant positive estimate (b = 2.6327, SE = 0.6080) scholars are
still more likely to collaborate with others from the same department.

H-Index:

Both an alter's and an ego's H-Index seem to be relevant in
collaboration preferences. The significant and positive estimateof AltX
(b = 0.0829, SE = 0.0364) suggest that scholars with higher h-index are
more preferred as collaborators. The egoX estimate is significant and
negative (b = -0.1591, SE = 0.0744) suggesting that scholars with higher
h-index are less likely to initiate collaborations.

*Discussion part about egoX h.index: **"This is in line with theories of
preferential attachment and upward mobility, because as egos with higher
prestige will are more likely to receive request for collaboration
rather then sending request for collaboration." - Niels***

The estimate for the Indegree Popularity weighted by h-index is
insignificant, suggesting that high-prestige individuals (as measured by
their h-index) do not significantly receive more indegrees

The results partially support **H4**, as the h-index is shown to
influence collaboration patterns, with prestigious scholars being more
likely to attract collaborations as alters but less likely to initiate
them as egos. However, gender homophily remains significant even after
controlling for the h-index, suggesting that prestige does not
substantially weaken the influence of gender homophily in co-authorship
networks.

Transitive Triplets (Diff Gender): A positive significant effect
(b=2.4871, SE = 0.6670). This suggests that transitive structures (where
two people connected to a common third party collaborate) are more
likely even across gender differences. Could be a potential
counterbalance to homophily.

R-Manual: in-degree popularity weighted by sender’s V (inPopX)
defined by the sum of values of V for actors h for which there are ties
i → j ← h

note that to use this effect for p = 2 the variable V must be
nonnegative, which
implies that it must be non-centered;
further note that if V is a behavioral variable, it will be used in the
centered version,
so that p must be 1; if weighting by a non-centered behavioral variable
is desired, a
new effect is necessary;
